\documentclass[10pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern,geometry,booktabs,amsmath,hyperref,xcolor}
\geometry{margin=2.1cm}
\hypersetup{colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black}
\newcommand{\teamname}{Marc Donovici}
\newcommand{\kaggleteam}{Marc Donovici (username \texttt{marcdonovici})}
\newcommand{\freezesha}{4db0ae5fd62c739a9398175c78e32add4f418a22}

\title{\textbf{The FREUID Challenge 2026}\\\large Technical Report --- \teamname}
\author{Marc Donovici\\\texttt{azerty10997@gmail.com}}
\date{13 July 2026}

\begin{document}
\maketitle

\begin{abstract}
We address binary identity-document fraud detection under cross-document, digital, and
print--capture domain shift. Our frozen submission is a no-TTA weighted rank ensemble of a
ConvNeXt-V2 Base detector (weight 0.75) and a DINOv2 ViT-B/14-with-registers detector (weight
0.25). The former supplies the strongest observed physical-recapture operating point; the latter
adds representations trained across unseen layouts and attack families. Recapture simulation is
applied to both classes, preventing capture appearance from becoming a fraud shortcut. Model
selection uses only official training data and a disjoint MIDV-Holo probe; private test images and
labels are never used for fitting or selection. A one-shot three-member training run was completed
before private release, but two auxiliary models collapsed on the unseen-attack probe and were
excluded. Per-template score normalization was also rejected after worsening the public FREUID
Score from 0.33816 to 0.54141 (lower is better). The public repository contains pinned weights,
source, an immutable-base Dockerfile, and an offline entrypoint that maps flat filenames in
\texttt{/data} to exactly \texttt{/submissions/submission.csv}.
\end{abstract}

\noindent\textbf{Competition:} FREUID Challenge 2026 (IJCAI--ECAI 2026)\\
\textbf{Kaggle team:} \kaggleteam\\
\textbf{Code:} \url{https://github.com/Marc-Dvci/FREUID}, frozen source commit
\texttt{\freezesha}

\section{Problem and metric}
FREUID targets bona-fide versus fraudulent identity documents, including physical manipulation,
generative editing, and print--capture attacks on document domains under-represented in public
benchmarks~\cite{freuid2026}. Labels are 0 for bona-fide and 1 for fraud; larger submitted scores
mean more likely fraudulent. The minimized FREUID Score is the harmonic combination of goodness
terms $1-\mathrm{AuDET}$ and $1-\mathrm{APCER}_{\mathrm{BPCER}=1\%}$. Consequently, a small tail of
high-scored bona-fides can be more damaging than average classification error suggests.

\section{Method}
\subsection{Selected detectors}
The selected ConvNeXt-V2 Base checkpoint uses the FCMAE ImageNet-22k/1k initialization
\cite{convnextv2}, a linear binary head, and $512\times512$ input (87,693,825 parameters). It was
fine-tuned with a leave-one-document-domain-out split, medium-strength recapture augmentation, and
gradient checkpointing during training. The selected DINOv2 model uses ViT-B/14 with
register tokens and LVD-142M initialization~\cite{dinov2}, a linear head, and $392\times392$ input
(86,133,505 parameters). Both produce one logit and use sigmoid probabilities before ensembling.

For a test set of $n$ images, each detector's probabilities are mapped to average ranks
$r_i\in[0,1]$; tied probabilities receive the same average rank. The final fraud score is
\begin{equation}
  s_i = 0.75\,r_i^{\mathrm{ConvNeXt}} + 0.25\,r_i^{\mathrm{DINOv2}}.
\end{equation}
These weights, checkpoints, and no-TTA policy were frozen before private-test release. Rank
combination controls incompatible calibration and limits influence from the less physically robust
DINOv2 member. Horizontal-flip TTA was rejected because it worsened DINOv2 on the full unseen probe
(FREUID 0.97752 to 0.99371).

\subsection{Training}
Training uses binary cross-entropy with logits, AdamW, cosine decay after a one-epoch warm-up,
automatic mixed precision, channels-last tensors, and seed 42. DINOv2 was fine-tuned for three
epochs with batch size 16, two-step gradient accumulation (effective batch 32), learning rate
$10^{-4}$, weight decay 0.01, and recapture probability 0.35. Epoch 2 was selected by the disjoint
OOD probe (checkpoint selection score 0.97484 on its fixed 3,000-row cap). The ConvNeXt checkpoint
used six epochs, batch size 8, four-step accumulation, learning rate $10^{-4}$, weight decay 0.01,
dropout 0.2, and recapture probability 0.6; its full arguments are embedded in the checkpoint.

The recapture transform models resize/upsample, repeated JPEG compression, blur, moir\'e,
halftoning, glare, vignetting, paper grain, colour cast, and sensor noise. It is sampled independently
for both classes. A pre-freeze one-shot run additionally trained ConvNeXt-V2 Base at 384 pixels and
a constrained Bayar/SRM ConvNeXt-V2 Nano forensic model. Their OOD outputs were near-constant; they
were excluded rather than allowed to create arbitrary filename-order ranks.

\section{Data and validation}
The official training release contains 69,352 samples from five document types (40,005 bona-fide,
29,347 fraud). Competition images are not redistributed. The DINOv2 run holds the 20 official
real-recapture rows out of fitting, reserves a fixed stratified 5\% monitoring split, and adds
15,179 MIDV-Holo frames to training (9,070 bona-fide, 6,109 fraud)~\cite{midvholo}. The external
training partition covers 14 documents and two attack families. A completely disjoint probe covers
6 other documents and 2 unseen attack families (6,428 rows); there is no shared image, clip, or
document identity. MIDV-Holo is CC BY-SA 2.5 and includes Generated Photos identities as documented
by its authors. Pretrained DINOv2 parameters are Apache-2.0; ConvNeXt-V2 pretrained parameters are
CC BY-NC 4.0. Full notices and URLs are in \texttt{THIRD\_PARTY\_NOTICES.md}.

The small 20-row official real-recapture slice is reported only as a stress test. Public leaderboard
feedback is a secondary sanity check because its domains and prevalence need not represent the
134,997-row private release. No public or private test image participates in training, adaptation,
clustering, or checkpoint selection.

\section{Results and ablations}
\begin{table}[h]
\centering\small
\caption{Pre-freeze evaluation (lower is better). The OOD probe uses all 6,428 rows.}
\begin{tabular}{lccc}
\toprule
Candidate / split & FREUID & AuDET & APCER@1\% BPCER\\
\midrule
DINOv2, unseen MIDV-Holo & 0.97752 & 0.50052 & 0.98850\\
ConvNeXt, unseen MIDV-Holo & 0.98288 & 0.54507 & 0.99127\\
Frozen 0.75/0.25 ensemble, unseen MIDV-Holo & 0.98672 & 0.54191 & 0.99326\\
ConvNeXt, official real-recapture stress & 0.10584 & 0.06548 & 0.14286\\
DINOv2, official real-recapture stress & 0.67570 & 0.40476 & 0.77714\\
Frozen 0.75/0.25 ensemble, real-recapture stress & 0.14890 & 0.08333 & 0.20571\\
\bottomrule
\end{tabular}
\end{table}

The conflicting probes motivate conservative weighting: DINOv2 is marginally best on new external
documents, whereas ConvNeXt is decisively better on the only official physical-recapture sample.
The existing ConvNeXt public submission scored 0.33816. Per-template clustering and within-template
normalization degraded it to 0.54141 and is disabled. The exact frozen ensemble public score remains
\textbf{pending Kaggle processing at report build time}; it must be filled before the final PDF.

\section{Inference and Docker reproduction}
Inference resizes and normalizes each image according to its checkpoint, uses FP16 autocast on CUDA,
and does not use TTA. The Docker entrypoint scans only supported image files directly below
\texttt{/data}; the identifier is the filename stem. It rejects empty input, duplicate stems,
missing weights, invalid ensemble weights, non-finite predictions, or any output path other than
\texttt{/submissions/submission.csv}. The output has exactly \texttt{id,label}; all labels are finite
in $[0,1]$. The root filesystem can be read-only, model creation uses
\texttt{pretrained=False}, CUDA kernel caching is disabled, and no runtime network or model cache is
needed.

\begin{verbatim}
git lfs install && git lfs pull
docker build -t freuid-repro:local .
docker run --rm --gpus all --network none --read-only \
  -v /path/to/flat/private_images:/data:ro \
  -v "$(pwd)/out:/submissions" freuid-repro:local
\end{verbatim}

The PyTorch base is pinned to the following digest:
\begin{center}\small\ttfamily
sha256:77f17f843507062875ce8be2a6f76aa6\\
aa3df7f9ef1e31d9d7432f4b0f563dee
\end{center}
Python dependencies are fully version-pinned. The private test set was scored by running this
container unchanged on the 134,997 released private images, under \texttt{--network none},
\texttt{--read-only}, a read-only \texttt{/data}, and a writable \texttt{/submissions}. The measured
wall-clock time was 131 minutes on one RTX 4070 (both members sequentially, batch 64, zero dataloader
workers), which is well below the organizer's six-hour A100 limit. Throughput is bound by
single-process image decoding rather than by the GPU, so a host with more dataloader workers will be
faster. Hashes and the image digest are recorded in \texttt{FINAL\_AUDIT.md}.

The selected public-row CSV retains placeholder 0.5 values for unreleased IDs. After private release,
the unchanged container runs on private images alone. \texttt{scripts/assemble\_final\_submission.py}
requires those IDs to equal exactly the official sample IDs minus the public-image stems, then replaces
only untouched private placeholders. It preserves official row order and validates the final hash,
schema, range, and finiteness.

\section{Reproducibility and integrity}
Training used one NVIDIA RTX 4070 (12 GB), PyTorch 2.6.0, CUDA 12.4, and seed 42. The full one-shot
three-model run took 292.8 minutes. Checkpoint SHA-256 values are:
\begin{itemize}
\item ConvNeXt selected: \texttt{aebf36acdf23dfe7a1542e9b07ba94e782910b547d6244f3fbb8d84083066510}.
\item DINOv2 selected: \texttt{f333c566bef9d6c2e9be8ba4a5b5efb5e708492e71162a135856a5e08ee1e8ca}.
\end{itemize}
cuDNN benchmarking can select nondeterministic convolution kernels, so bitwise retraining is not
claimed; submitted weights and inference are fixed. The repository contains no competition images,
external images, credentials, or runtime download logic.

\section{Team and contributions}
Marc Donovici performed data preparation, model development, validation, container engineering, and
reporting, and is the sole entrant.

\bibliographystyle{plain}
\bibliography{references}
\end{document}
